---
title: "Coursera Leaflet Map Assignment"
author: "JB"
date: "January 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Map of Toronto

This assignment shows a map of downtown Toronto created with the R leaflet package.
A thumbs up icon was created from a .png file and displayed at city hall.
A label is shown indicating Toronto. Also, some circle markers
were added to show subway station locations in the area. The stations on the Yonge 
and University subway lines are shown as red and blue circle markers, respectively.  
Union Station connects both lines, so the overlap of the circle markers creates a 
purple marker.  A legend is also provided showing the Yonge and University 
line stations.
```{r toronto_leaflet_map}
library(leaflet)


yonge_subway_stations <- data.frame(lat =c(43.6491,43.6525,43.656389,43.661389, 43.645556),
                              lng = c(-79.3781,-79.379167,-79.38033,-79.383056,-79.380556))

uni_subway_stations <- data.frame(lat = c(43.647778,43.650833,43.654722,43.66,43.645556),
                          lng = c(-79.384722,-79.386667,-79.388333,-79.390556,-79.380556))


thumbs_up <- makeIcon("Thumbs_up.png", iconWidth = 60,iconHeight=60,
                      iconAnchorX = 30, iconAnchorY = 30)

toronto_map <- leaflet() %>% addTiles() %>%
  addMarkers(lat=43.6532, lng=-79.3832, 
             icon = thumbs_up, label = "Toronto (best city around)",
             labelOptions=labelOptions(noHide=T, direction = "left", offset = c(50,0),
                          textsize="25px",
             style = list("color" = "magenta",
                          "font-family"="serif",
                          "font-style"="italic",
                          "border-color" = "rgba(1,1,1,0.1)"))) %>%
  addCircleMarkers(yonge_subway_stations$lng, yonge_subway_stations$lat, color = 'red') %>%
  addCircleMarkers(uni_subway_stations$lng,uni_subway_stations$lat, color = 'blue') %>%
  addLegend(labels = c("Yonge line", "University line"), colors = c("red", "blue"))

toronto_map
```

